
% ----------------------------------------------------------
% Anexos
% ----------------------------------------------------------
%
% ---
% Inicia os anexos
% ---
\begin{anexosenv}

% Imprime uma página indicando o início dos anexos
%\partanexos




%----------------------------------------------------------------------------XXXX


\chapter{Children’s Knowledge of Abuse Questionnaire Revised – III}\label{chap:CKAQ}


\noindent
\textbf{I.D. Number: \rule{5.4cm}{0.15mm} \quad Age: \rule{2.5cm}{0.15mm} \quad Boy \makebox[0pt][l]{$\square$}{}  \quad  or Girl \makebox[0pt][l]{$\square$}{}}

\vspace{1.0cm}

\noindent
\textbf{Please respond T for "True", F for "False", and DK for "Don't Know", to the following
questions:}



%\makebox[0pt][l]{$\square$}{\raisebox{0.1\height}{$\times$}} = Esse é o quadrado com o X dentro

\begin{enumerate}
	\item You always have to keep secrets.
	\item It's OK for someone you like to hug you.
	\item You can always tell who's a stranger - they look mean.
	\item Most kids like to get a kiss from their parents before they go to bed at night, so, for them, that would be a good touch.
	\item Sometimes it's OK to say no'' to a grown-up.
	\item It's OK to say ``no'' and move away if someone touches you in a way you don't like.
	\item Even if someone say that they know you, if you don't know them they're a stranger.
	\item Even hugs and tickles can turn into bad touches if they go on too long.
	\item If you fell off your bike and hurt your private parts, it would be OK for a doctor or nurse to look under your clothes.
	\item If someone touches you in a way you don't like, you should tell someone you trust.
	\item If your friend says he won't be your friend any more if you don't give him your last piece of candy, then you should give it to him.
	\item If someone touches you in a way you don't like, it's your own fault.
	\item If you don't like how someone is touching you, it's OK to say ``no''.
	\item Strangers look like ordinary people.
	\item If a grown-up tells you to do something you always have to do it.
	\item Some touches start out feeling good, then turn confusing.
	\item You can trust your feelings about whether a touch is good or bad.
	\item It's OK to have a hug from a grown-up you like.
	\item If a mean kid at school orders you to do something you had better do it.
	\item Even someone you like could touch you in a way that feels bad.
	\item A pat on the back from a teacher you like after you've done a good job at school is a good touch.
	\item You have to let grown-ups touch you whether you like it or not.
	\item If someone touches you in a way that does not feel good, you should keep on telling until someone believes you.
	\item Sometimes someone in your family might touch you in a way you don't like.
	\item Boys don't have to worry about someone touching their private parts.
	\item If you're walking down the street with your mother and she starts talking to a neighbour you have not met before, it's OK to talk with them too.
	\item If a friend's dad asks you to help him find their lost cat, you should go right away with him and help.
	\item If you won a contest for drawing the best picture in your school and a neighbour you liked gave you a quick hug to congratulate you, that would be a good touch.
	\item Most people are strangers and most strangers are nice.
	\item Someone you know, even a relative, might want to touch your private parts in a way that feels confusing.
	\item If your baby-sitter tells you to take off all your clothes but it's not time to get undressed for bed, you have to do it.
	\item If someone walks in while you are having a bath, and you feel uncomfortable, you should just keep quiet.
	\item If you get separated from your parents in a shopping mall, it's OK to ask a sales clerk or a security guard for help, even if they are strangers. 
\end{enumerate}



%----------------------------------------------------XXXXXXXXXXXXXXXXXXXXXxx



\end{anexosenv}
